Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2024-06-12 manuscript/manuscript.tex
Add MKGs conflic of interest
Add python package/notebook notice to abstract

In this tutorial, we aim to guide the reader through the most common steps involved in a GIST analysis using the streptavidin-biotin complex as an demonstrative system.
Furthermore, we discuss the theory of GIST with a focus on practical aspects.
We highlight potential pitfalls and show how to avoid technical difficulties.
We assume familiarity with molecular dynamics simulations as well as the AmberTools  package \cite{Case2023-ambertools}.

@@

Declare any potentially conflicting interests here, whether or not they pose an actual conflict in your view.

>>>>

In this tutorial, we aim to guide the reader through the most common steps involved in a GIST analysis using the streptavidin-biotin complex as an demonstrative system. Towards this, Jupyter notebooks and python packages are provided to simplify the analysis.
Furthermore, we discuss the theory of GIST with a focus on practical aspects.
We highlight potential pitfalls and show how to avoid technical difficulties.
For this tutorial, familiarity with molecular dynamics simulations as well as the AmberTools package \cite{Case2023-ambertools} is assumed.

@@

MKG has an equity interest in and is a cofounder and scientiﬁc advisor of VeraChem LLC.
